---
title: "MA331-Report: 2212188"
subtitle: "TED Talks by Speaker Dong Woo Jang and Speaker Stephen Hawking"
author: "Channagiri Nagaraja, Ranjitha"
output: html_document
---

```{r setup, include=FALSE}
### Don't delete this setup code chunk from your file
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, comment = NULL)   ## DON'T ALTER THIS: this is to prevent printing the code or any unnecessary addition in your final "html" report file.

# You can extend this list below to load all the packages required for your analyses:
#====================================================================================
# load the data
library(dsEssex)    #load the dsEssex package
library(tidyverse)  #load the tidyverse package
library(tidytext)   #load the tidytext package
library(dplyr)      #load the dplyr package
library(ggplot2)    #load the ggplot2 package
library(ggrepel)    #load the ggrepel package
library(tidyr)      #load the tidyr package

# load the 'ted_talks' data
#=========================
data(ted_talks)

load(file = "ted_talks.rda")

#display few rows
head(ted_talks)

#tidying and Tokenisation
#unnest_tokens tokenizes the individual words and creates a new row from ted_talks dataset and stores it in variable tidy_talks 
tidy_talks <- ted_talks %>% 
  unnest_tokens(word, text)  

#Stopwords removal
#anti_join() function removes stop words from tidy_talks and stores it in Mydata
Mydata <- tidy_talks %>% 
  anti_join(get_stopwords())


#Identification of top words for Dong_Woo_Jang speaker
Jang_words <- Mydata %>%
  #filters only rows of speaker of Dong Woo Jang
  filter(speaker == "Dong Woo Jang") %>% 
  #counts the frequency of words in Jang's talks, sort = TRUE describes descending order
  dplyr::count(speaker, word, sort = TRUE) 

#Visualisation of top words
Jang_ggplot <- Jang_words %>%
  #slice_max is used to keep top words, "n" specifies new column which holds top 25 rows         
  dplyr::slice_max(n,n=25) %>%
  #mutate is used to reorder words by frequency count using the 'reorder()' ,that takes two arguments 'word' and 'n'
  dplyr::mutate(word = reorder(word,n)) %>%
  #This creates new plot with 'n' as xx-axis and 'word' as y-axis
  #geom_col() creates the bar chart and ggtitle() adds title
  ggplot2::ggplot(aes(n, word)) + ggplot2::geom_col() + ggtitle("Dong Woo Jang")


#identification of top words for Hawking
Hawking_words <- Mydata %>%
  #filtering speaker 'stephen Hawking'
  filter(speaker == "Stephen Hawking") %>%
  #counts the frequency of each unique word 
  dplyr::count(speaker, word, sort = TRUE)


#Visualisation of top words
Hawking_ggplot <- Hawking_words %>%
  #slice_max is used to keep top words, 'n' specifies new column which holds top 25 rows
  dplyr::slice_max(n, n=25) %>%
  #mutate is used to reorder words by frequency count using the 'reorder()' ,that takes two arguments 'word' and 'n'
  dplyr::mutate(word = reorder(word, n)) %>%
  #This creates new plot with 'n' as xx-axis and 'word' as y-axis
  #geom_col() creates the bar chart and ggtitle() adds title
  ggplot2::ggplot(aes(n, word)) + ggplot2::geom_col() + ggtitle("Stephen Hawking")


#comparison between two speaker
Comparing <-dplyr::bind_rows(Jang_words, Hawking_words) %>%
  #group all data frame by the word
  group_by(word) %>%
  #filter() function keeps only rows where sum of frequency counts for word is greater than 10
  filter(sum(n) > 10) %>%
  #ungroup()  removes the grouping so that data frame can be in wide for mat
  ungroup() %>%
  #pivots the data frame in wide format
  pivot_wider(names_from = "speaker", values_from = "n", values_fill = 0) %>%
  #creates a new plot where x-axis is speaker 1 and y-axis is speaker 2
  ggplot(aes("Dong Woo Jang", "Stephen Hawking")) +
  #geom_abline() adds diagonal reference line
  geom_abline(color = "Blue", size = 1.5, alpha = 1, lty = 3)+
  #adds the text label of each word with the label argument specifying the column 'word'
  geom_text_repel(aes(label=word), max.overlaps = 15)+
  #fixes the aspect ratio of the plot
  coord_fixed()

#odds ratio and sentimental analysis
Jang_analysis <- Jang_words %>%
  #used to join each data frame
  inner_join(get_sentiments("bing"))
Hawking_analysis <- Hawking_words %>%
  inner_join(get_sentiments("bing"))


#bind_rows() used to combine the rows of two data frames
#mutate() adds a new column 'person' to each data frame
data1 <- bind_rows(Jang_words %>% mutate(person = "Jang"),
                   Hawking_words %>% mutate(person = "Hawking"))


#count the sentiments per person and displaying in wide format
senti_wider <- data1 %>%
  #data1 is joined with bing sentiment lexicon using inner_join()
  inner_join(get_sentiments("bing")) %>%
  #counts the number of occurrences of each sentiment for each speaker
  count(person, sentiment) %>%
  #the result is transformed from long format to a wide
  pivot_wider(names_from = person, values_from = n, values_fill = 0) %>%
  #odds ratio and log odds ratio are computed using dsEssex:::compute_OR()
  mutate(OR = dsEssex:::compute_OR(Jang, Hawking, correction = FALSE), log_OR=log(OR),
 #reorder() is rearranged by log odds ratio        
sentiment = reorder(sentiment, log_OR)) %>%
  #a plot is created using ggplot() 
  ggplot(aes(sentiment, log_OR, fill = log_OR < 0)) +
  #geom_col() is used to create a bar plot
  geom_col(show.legend = FALSE) +
  #yaxis is labeled
  ylab("Log odds ratio") +
  #title will be 'sentimental analysis'
  ggtitle("Sentimental analysis") +
  coord_flip() +
  #the color of the bars is set to 'darkgreen' and 'red'
  scale_fill_manual(name = "", values = c("darkgreen","red"))

#jang_analysis is grouped by sentiment
Top_Jang_words <- Jang_analysis %>%
  group_by(sentiment) %>%
  #slice_max is used to select top 10 words
  slice_max(n, n=10) %>%
  mutate(word = reorder(word,n)) %>%
  #returns all the data to non-grouped
  ungroup()

#creates a bar plot of top 10 words used by Dong Woo Jang with 'n' as x-axis and 'word' as y-axis
PN_Jang_Words <- ggplot(Top_Jang_words, aes(n,word, fill = sentiment)) +
  #geom_col() represents height of the bar
  geom_col(show.legend = FALSE) +
  #facet_wrap() separates panel for each sentiment ,scales ensures that the scales of the y-axis are free
  facet_wrap(~sentiment, scales = "free") +
  #title will be 'Dong Woo Jang'
  ggtitle("Dong Woo Jang")

#Hawking_analysis is grouoed by sentiment
Top_Hawking_words <- Hawking_analysis %>%
  group_by(sentiment) %>%
  #slice_max selects top 10 words
  slice_max(n,n=10) %>%
  mutate(word = reorder(word,n)) %>%
  #returns all the data to non-grouped
  ungroup()

#creates a bar plot of top 10 words used by Stephen Hawking with 'n' as x-axis
PN_Hawking_words <- ggplot(Top_Hawking_words, aes(n, word, fill= sentiment)) +
  #geom_col() represents height of the bar
  geom_col(show.legend = FALSE) +
  #facet_wrap() separates panel for each sentiment, scales ensures that the scales of the y-axis are free
  facet_wrap(~sentiment, scales = "free") +
  #title will be 'Stephen Hawking'
  ggtitle("Stephen Hawking")

```

## Introduction

  My first speaker Dong Woo Jang who turns a stick of bamboo into an archer's bow. He spent the first three years developing a habitat for spiders in his room while studying their anatomy and hunting techniques.He gave the speech in the year of 2013.
  My second speaker Stephen Hawking a popular well-known physicist and cosmologist frequently discusses subjects connected to his study, such as black holes, the beginnings of the cosmos, and the origin of the universe.The talk was given by Stephen Hawking in April 2008.

## Methods

This R code is intended to examine the key phrases said by Dong Woo Jang and Stephen Hawking, two separate presenters in TED Talks.
The following packages are loaded in the first line of the code: dsEssex, tidyverse, tidytext, dplyr, ggplot2, ggrepel, and tidyr.
The TED Talks dataset is loaded in the next section, which then uses the head() method to display a few rows.
The dataset is cleaned up and tokenized in the third part using the unnest_tokens() method, which adds a new row to the dataset's text column for each distinct word. A new variable named tidy_talks is created as a result.

The anti_join() function, which eliminates frequent words that don't add sense to a phrase, is used in the fourth section to remove stopwords. The result is saved in a new variable named Mydata.
In the fifth and sixth parts, ggplot2 is used to make bar charts showing the top terms used by Dong Woo Jang and Stephen Hawking, respectively. Only the top 25 words are kept by the slice_max() method, and the modify() function reorders the words according to frequency counts.
The seventh section creates a comparison plot between the two speakers using the bind_rows(), group_by(), filter(), ungroup(), and pivot_wider() functions to combine the top words dataframes and present them in a wide format. This plot includes a diagonal reference line and text labels for each word.
Finally, the last section performs an odds ratio and sentiment analysis using the inner_join() function and the get_sentiments() function, respectively. It also creates a count of the number of occurrences of each sentiment for each speaker using the count() function and presents the data in a wide format using the pivot_wider() function.


## Results
                              LEVEL 1 - Summary and word counts

```{r fig.width=3, fig.height=4}
#word count of speaker Dong Woo Jang
Jang_ggplot 
```
```{r fig.width=3, fig.height=4}
#word count of speaker Stephen Hawking
Hawking_ggplot
```
```{r fig.width=2, fig.height=2}
#summary of both the speakers
summary(Jang_words);summary(Hawking_words)
```
                   
                          LEVEL 2 - Comparisons between the two speakers'
```{r fig.width=3, fig.height=2}
#comparing the common words used by the speakers
Comparing
```

  

      LEVEL 3 - Deeper comparisons between the two speakers, using numerical and visualize techniques
  
```{r fig.width=2, fig.height=1}
#sentimental analysis of Dong Woo Jang
Jang_analysis
```
```{r fig.width=2, fig.height=1}
#sentimental analysis of Hawking Speaker
Hawking_analysis
```
```{r fig.width=3, fig.height=3}
#Analysis of positive and negative words
senti_wider
```
```{r fig.width=4, fig.height=3}
#sentimental analysis through visualization
PN_Jang_Words
```
```{r fig.width=4, fig.height=3}
#sentimental analysis through visualization
PN_Hawking_words
```

     LEVEL 4 - Interpretations and explanations on the general findings and comparisons


   The code in level 3 is performing sentimental analysis on two sets of data Dong Woo Jang and Stephen Hawking respectively. The code contains positive and Negative words which uses the "bing" lexicon for sentimental analysis.
   The line illustrates the language they used, both positively and negatively.Dong Woo Jang, the first speaker, used far more positive terms than negative ones when describing how he transformed a stick of bamboo into an archer's bow.He frequently used positive words like "works well," "survival","ideal," "great," "effective," "better," etc. The other speaker, Stephen Hawking, who discusses the universe's beginnings, also used much more encouraging language, such as "thank you," "progress," "like," "good," and "survival," among other terms.
    
    